\documentclass[letterpaper,11pt]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}

% Margins

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections Formatting

\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom Commands
    \newcommand{\resumeItemSmall}[2]{
        \item[]
        \small{
            \textbf{#1}{: #2 \vspace{-2pt}}
        }
    }

    \newcommand{\resumeItem}[2]{
    \item
    \small{
        \textbf{#1}{: #2 \vspace{-2pt}}
    }
    }

    \newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item[]
        \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
        \end{tabular*}\vspace{-5pt}
    }

    \newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
    \newcommand{\resumeSubItemSmall}[2]{\resumeItemSmall{#1}{#2}\vspace{-4pt}}
    \renewcommand{\labelitemii}{$\circ$}
    \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
    \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
    \newcommand{\resumeItemListStart}{\begin{itemize}}
    \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%%%%%%%% CV STARTS HERE %%%%%%%%%%%%%%% 

\begin{document}
    
    % Heading
        \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
            \textbf{\LARGE Jacob Enriquez} \\
            \href{https://www.linkedin.com/in/jacob-enriquez/}{https://www.linkedin.com/in/jacob-enriquez/} & jyenriquez@gmail.com \\
            \href{https://github.com/jyenriquez}{https://github.com/jyenriquez} & 484-467-8092 \\
            
        \end{tabular*}

    % Experience
        \section{Experience}
         \resumeSubHeadingListStart

                \resumeSubheading{J.P. Morgan Chase}{Wilmington, DE}{Software Engineer, Full-Stack}{Full Time, July 2022 - Now}
                \resumeItemListStart
                    \resumeItem{React.js, Jest}{Worked on developing features in a Linux environment heavily reliant on proprietary command line interface tools to use Docker containerized environments for development}
                    \resumeItem{Java, Springboot Framework, Maven}{Designed, tested, and developed backend web services to create reusable software artifacts to act as building blocks to unify all Boomi products utilizing Spring Framework concepts such as aspect oriented programming}
                    \resumeItem{Private Cloud}{Deployed features to test environments using Jenkins Build pipeline on JPMorgan Chase's private cloud infrastructure, ensuring seamless integration and rigorous testing for optimal functionality during feature development.}
                    \resumeItem{Selenium, REST Assured}{Designed, tested, and developed backend web services to create reusable software artifacts to act as building blocks to unify all Boomi products utilizing Spring Framework concepts such as aspect oriented programming}
                    \resumeItem{JUnit, Mockito}{Utilized test driven development strategies to develop reliable code for features by testing against software requirements in integration tests and unit tests in Java testing frameworks}
                \resumeItemListEnd

                \resumeSubheading{Xandr}{Remote}{Software Engineer, Front-End}{Internship, June 2021 - Aug 2021}
                \resumeItemListStart
                    \resumeItem{React.js}{Worked as a Software Engineer Intern in Xandr’s InvestDSP department. Developed front-end interfaces
                    and unit tests for Buyer Monitoring and Troubleshooting. Responsible for helping users understand what they
                    spend on and how to troubleshoot.}
                    \resumeItem{Jest Testing Framework}{Wrote Tests for React development to reach desired code coverage specified in SonarQube.}
                    \resumeItem{GraphQL}{Implemented custom queries to fetch specific item data.}
                    \resumeItem{Agile}{Developed features in 2 week sprints, featuring daily stand-ups, and backlog/assignment tracking in JIRA.}


                \resumeItemListEnd

            \resumeSubHeadingListEnd
    
    % Projects
        \section{Projects}

            \resumeSubHeadingListStart
                \resumeSubItemSmall{SEPTA Discord Bot}{Created a Java-based bot with Spring Boot and JDA, allowing users to check schedules for Southeastern Pennsylvania stations and receive notifications for approaching trains.}
                \resumeSubItemSmall{Terra Rogue}{Developed an RPG game with a team using Java and LibGDX. Contributed to core gameplay mechanics, character interactions, and visuals.}
                \resumeSubItemSmall{Acufuncture}{Collaborated on a team project to create a web app for user interaction through "pokes." Implemented user account management using Google Cloud Platform's Datastore. Developed with Python, Flask, and utilized vanilla JavaScript, HTML, and CSS.}
                % \resumeSubItemSmall{Local Ubuntu Server}{Repurposed old computer components to create a local network Ubuntu Server running version 20.04.}
            \resumeSubHeadingListEnd

    % Education
    \section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
        {University of Pittsburgh}{Pittsburgh, PA}
        {Bachelor of Science in Computer Science; GPA: 3.65}{August 2018 - April 2022}
    \resumeSubHeadingListEnd

    % Education
    \section{Certifications}
    \resumeSubHeadingListStart
        \resumeSubheading
        {AWS Certified Cloud Practitioner}{Foundational}
        {Fundamental Proficiency in AWS Services and Terminology}{February 2023 - February 2026}
    \resumeSubHeadingListEnd

    % Skills
        \section{Skills}
            \resumeSubHeadingListStart
            \item[]{
                \textbf{Languages}{: JavaScript, TypeScript, Java, SQL, Python, HTML, CSS}
                \hfill \\
                \textbf{Frameworks/Libraries}{: React.JS, Springboot, JUnit, Jest, Selenium, REST Assured} \\
                \textbf{Server Operating Systems}{: Ubuntu CLI 20.04} \\
                \textbf{Public Cloud}{: Amazon Web Services} \\
                \textbf{Private Cloud}{: Proprietary Private Cloud at J.P. Morgan} \\
                \textbf{Collaboration Tools}{: Jenkins, Git/Bash, Atlassian JIRA, Confluence} \\
            }
            \resumeSubHeadingListEnd

\end{document}